---
title: "Visualization Report"
author: "Shubhashish MDS202239"
date: "2022-11-02"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Abstract

The following report contains the graphical analysis of data containing Amsterdam house prices.

# Data Description





```{r message = FALSE}


library(ggplot2)

library(tidyverse)

hspd<- as.data.frame(read.csv("C:/Users/Shubhashish/Desktop/hspd.csv"))

VariableName = c('Address', 'Zip', 'Price' ,'Area' ,'Room', 'Lon' ,'Lat')

VariableType = c('Alphanumeric(Nominal)', 'Alphanumeric(Nominal)', 'Numeric(Continuous)' , 'Numeric(Continuous)', 'Numeric(Discrete)', 'Numeric(Continuous)', 'Numeric(Continuous)')

Description = c("Residential address", "Residential Zip code", "Residential price in Euros", "Residential area in square meters","Number of rooms at residence", "Longitude coordinates", "Latitude coordinates")

variable = data.frame(VariableName, VariableType, Description)


knitr::kable(variable, "pipe", col.name = c("Variable Name", "Variable Type", "Description"), align = c("l", "c", "c", "c","c","c","c"))

```







```{r message=FALSE}



ahspd = as.data.frame(na.omit(hspd))


ahspd = as.data.frame(na.omit(hspd))

ggplot(ahspd, aes(x=Area, y=Price))+geom_point()+scale_x_continuous(trans='log2') +
  scale_y_continuous(trans='log2') +theme_classic() + ggtitle('Price vs Area on Log scale') + geom_smooth(method = 'lm')

```
\large
We can observe that price and area of a house are highly correlated 

```{r}

ggplot(ahspd, aes(x=Lon, y=Lat,colour=Price/Area))+geom_point()+theme_classic()+ theme(panel.background = element_rect(fill = "black"))+ scale_colour_gradient(low="blue", high="yellow")+xlab(label = 'Longitude')+ylab(label = 'Latitude')+ggtitle(label = 'Location of the houses compared to their Price per unit Area')

```
\large
We can see the houses in the central region are more expensive per unit area.
```{r}
room_stat = ahspd%>%
  group_by(Room)%>%
  summarise(mean_price_per_unit_area=sum(Price)/sum(Area))



ggplot(data =  room_stat, aes(x=factor(Room), y=mean_price_per_unit_area)) + geom_col() +ggtitle(label = 'Average Price per unit Area vs Number of Rooms') + xlab(label = "Number of Rooms")+ ylab(label = "Average Price per unit Area")+theme_classic()

```
\large
Average Price per unit area of houses with 10, 13 and 14 rooms is highest, which suggests that these are luxury houses.
